Packet Optical Transport Network Slicing with Hard and Soft Isolation

### 2021-06-27 rebuttal_1.tex

%% journalrebuttal.tex
%% Copyright 2020 Pranav Hosangadi
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Pranav Hosangadi.
%
% This work consists of the file journalrebuttal.cls and the demo
% file journalrebuttal.tex
%% 
%%
%% journalrebuttal.tex
%% Example usage for journalrebuttal.cls: 
%%    A LaTeX class to create rebuttal documents for journal
%%    reviews
%% Created: 2020-06-28
%% Author: Pranav Hosangadi (pranav.hosangadi@gmail.com)
%% https://github.com/pranavh/JournalRebuttal_LaTeX
%% Last Modified: 2020-06-29
%% Version: 1.0
%%
\documentclass[12pt]{journalrebuttal}

\title{Packet Optical Transport Network Slicing with Hard and Soft Isolation}

\author{S.~Barguil, V.~López, L.M.~Contreras, O. González de Dios, A.~Alcalá, C.~Manso, P.~Alemany, R.~Casellas, R.~Martínez, D.~González-Pérez, X. Liu, J.M.~Pulido, J.P. Fernández-Palacios, R.~Muñoz, R.~Vilalta}

\journal{Applied Sciences}
\manuscriptid{applsci-1270422}

\usepackage{verbatim}
\usepackage{changes}
%% You can define Note commands using the \ColorNote command 
%% provided in the class. 
\newcommand{\PHNote}[1]{\ColorNote{red}{PH}{#1}}

\begin{document}
%\pagenumbering{arabic}
\maketitle

\vspace{0.5cm}
\makerule
\section*{Overview}

We would like to thank the reviewers for the fruitful feedback as well as their time to carry out the review. We have incorporated most of their suggestions, which have resulted in a significant improve of the paper.

\nextreviewer

\begin{revcomment}
This work focuses on studying the uses and validates of iFusion architecture defined by Telefonica. Which works on the validation of an end-to-end creation, modification and deletion of transport network slices with several degrees of isolation.

The presentation, exhibition and the results are well commented on in the text and the bibliography describes well the background on the subject matter and the contributions of the research group.  
However, there are some requirements before publishing:
\end{revcomment}

\begin{revcomment}
English and grammatical errors should be rectified during the revision of the paper.
\end{revcomment}

\begin{response}
Thank you for the comment.  The authors have corrected typos and proofread the document to improve English usage and readability.
\end{response}

\begin{revcomment}
The authors should also add the definition of abbreviations in the text, that some abbreviations are not defined. Eg.: BSS/OSS\_line3, YANG\_line11, L3VPNs\_line34, VPN\_line95, ODus-line113, etc.
\end{revcomment}

\begin{response}
The authors enhanced the \Cref{tab:abbreviations} of the abbreviation to include the whole set of abbreviations and facilitate the paper understanding.

\begin{table}[htb!]
\caption{List of abbreviations used across the document}
\label{tab:abbreviations}
\begin{center}
\begin{tabular}{|l|l|}
\hline
Abbreviation & \multicolumn{1}{c|}{Definition}              \\ \hline
3GPP         & 3rd Generation Partnership Project           \\ \hline
API          & Application programming interface            \\ \hline
\added{BSS}  & \added{Business Support System}              \\ \hline
\added{BGP}  & \added{Border Gateway Protocol}              \\ \hline
\added{CE}   & \added{Customer Edge}                        \\ \hline
IETF         & Internet Engineering Task Force              \\ \hline
eMBB         & Enhanced Mobile Broadband                    \\ \hline
L2SM         & L2VPN Service Model                          \\ \hline
L2NM         & L2VPN Network Model                          \\ \hline
L3SM         & L3VPN Service Model                          \\ \hline
L3NM         & L3VPN Network Model                          \\ \hline
\added{L3VPN}  & \added{Layer Three Virtual Private Network}\\ \hline
MC           & Mobile Core                                  \\ \hline
mMTC         & Massive Machine Type Communication           \\ \hline
MPLS         & Multiprotocol Label Switching                \\ \hline
NASS         & Network As A Service                         \\ \hline
NGMN         & Next Generation Mobile Networks              \\ \hline
NSI          & Network Slice Instance                       \\ \hline
\added{ODU}  & \added{Optical Distribution Unit}            \\ \hline
ONF          & Open Networking Foundation                   \\ \hline
OSS          & Operation Support Systems                    \\ \hline
\added{PE}   & \added{Provider Edge}                        \\ \hline
QoS          & Quality of service                           \\ \hline
RAN          & Radio Access Network                         \\ \hline
SDN          & Software Defined Network                     \\ \hline
SI           & Service Instance                             \\ \hline
URLLC        & Ultra Reliable Low Latency Communications    \\ \hline
VSI          & Virtual switching Interfaces                 \\ \hline
\added{VPN}  & \added{Virtual Private Network}              \\ \hline
VRF          & Virtual Routing and Forwarding              \\ \hline
YANG         & Yet Another Next Generation                  \\ \hline
\end{tabular}
\end{center}
\end{table}

Furthermore, in the text some abbreviations was expanded to enhance the readability:

\added{Thus, VRFs, VSIs or \added{Optical Data units} (ODus) cannot be managed by their corresponding tenants directly because they are part of the same administrative domain represented by the physical device, and they need to be operated by the network administrator.}
\end{response}

\begin{revcomment}
Line 66 , "..ecosystem [9–11]., One.." Delete the extra comma "
\end{revcomment}

\begin{response}
The authors replaced some minor nits found in the paper.
\end{response}

\begin{revcomment}
Lines 73-78, Very long sentence and confused!!
\end{revcomment}

\begin{response}
The authors has rephrased the sentence to enhance the readability:

\added{5G expects to support a new generation of customer-tailored applications with diverse requirements regarding capacity, latency, level of mobility, number of users, and user density.  Hence, 5G sets the stage for innovation and transformation in customer services and vertical industries, such as the ones described in the Table 2 [12].}

\end{response}

\end{document}

### 2021-06-27 template.tex
Updates from Overleaf

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{cleveref}
\usepackage{enumitem}
%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

@@

\begin{table}[htb!]
\caption{List of abbreviations used across the document}
\label{tab:abbreviations}
\begin{tabular}{|l|l|}
\hline
Abbreviation & \multicolumn{1}{c|}{Definition}              \\ \hline
3GPP         & 3rd Generation Partnership Project           \\ \hline
API          & Application programming interface            \\ \hline
IETF         & Internet Engineering Task Force              \\ \hline
eMBB.        & Enhanced Mobile Broadband                    \\ \hline
L2SM         & L2VPN Service Model                          \\ \hline
L2NM         & L2VPN Network Model                          \\ \hline
L3SM         & L3VPN Service Model                          \\ \hline
L3NM         & L3VPN Network Model                          \\ \hline
MC           & Mobile Core                                  \\ \hline
mMTC         & Massive Machine Type Communication           \\ \hline
MPLS         & Multiprotocol Label Switching                \\ \hline
NASS         & Network As A Service                         \\ \hline
NGMN         & Next Generation Mobile Networks              \\ \hline
NSI          & Network Slice Instance                       \\ \hline
ONF          & Open Networking Foundation                   \\ \hline
OSS          & Operation Support Systems                    \\ \hline
QoS          & Quality of service                           \\ \hline
RAN          & Radio Access Network                         \\ \hline
SDN          & Software Defined Network                     \\ \hline
SI           & Service Instance                             \\ \hline
URLLC        & Ultra Reliable Low Latency Communications    \\ \hline
VSI          & Virtual switching Interfaces                 \\ \hline
VRF          & Virtual Routing and Forwarding.              \\ \hline
YANG         & Yet Another Next Generation                  \\ \hline
\end{tabular}
\end{table}

@@

The network slicing concept provides a framework for broad applicability across various industries. The majority of these scenarios envisioned to suit emerging and diverse business models based on the Network As A Service (NASS) approach, creating opportunities for intelligent services and a new business ecosystem \cite{kuklinski2019business,zhang2017network,khan2020network}., One of the main enablers to drive the network slicing is the Fifth-generation (5G) networks realization. Due to the necessity to integrate multiple services with various performance requirements — such as high throughput, low latency, high reliability, high mobility, and high security — into a single physical network infrastructure, and provide each service with
a customized logical network. being the Network Slicing the key technology to achieve the aforementioned goals.

Due to the 5G expectation of supporting of a new generation of customer-tailored applications with diverse and stringent requirements (e.g., in terms of capacity, latency, level of mobility, number of users, and user density), 5G sets the stage for innovation and transformation in consumer services and vertical industries, such as real-time services, location-based services, and mission-critical services, as the ones described in the \cref{TAB1} \cite{foukas2017network}.

\begin{table}[htb!]
\caption{TAB1:}
\label{TAB1}
\centering
\begin{tabular}{|l|l|l|}
\hline

@@

Despite the apparent advantages that an overlay MPLS tunnels could provide, there are some disadvantages. Overlay tunnels built by data encapsulation have neither visibility nor control of the underlying physical network. With more and more tunnels deployed on shared physical infrastructure, network congestion necessarily becomes an attention point.  Thus, VRFs, VSIs or ODus cannot be managed by their corresponding tenants directly because they are part of the same administrative domain represented by the physical device, and they need to be operated by the network administrator. Due to the massive number of tunnels and services in a complex network, the QoS and Traffic Engineering policies management becomes a crucial task to guarantee the right SLAs to its customers \cite{huang20205g,marotta2020reliable}.

@@

\begin{itemize}
    \item  \textit{Map & Realize}:The mapping and realization can be done by the Domain controller applying the service logic to create policies directly on the Network elements.
\end{itemize}

@@

@@

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{changes}
%\usepackage[final]{changes}
%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

@@

\begin{table}[htb!]
\caption{List of abbreviations used across the document}
\label{tab:abbreviations}
\begin{tabular}{|l|l|}
\hline
Abbreviation & \multicolumn{1}{c|}{Definition}              \\ \hline
3GPP         & 3rd Generation Partnership Project           \\ \hline
API          & Application programming interface            \\ \hline
\added{BSS}  & \added{Business Support System}              \\ \hline
\added{BGP}  & \added{Border Gateway Protocol}              \\ \hline
\added{CE}   & \added{Customer Edge}                        \\ \hline
IETF         & Internet Engineering Task Force              \\ \hline
eMBB         & Enhanced Mobile Broadband                    \\ \hline
L2SM         & L2VPN Service Model                          \\ \hline
L2NM         & L2VPN Network Model                          \\ \hline
L3SM         & L3VPN Service Model                          \\ \hline
L3NM         & L3VPN Network Model                          \\ \hline
\added{L3VPN}  & \added{Layer Three Virtual Private Network}\\ \hline
MC           & Mobile Core                                  \\ \hline
mMTC         & Massive Machine Type Communication           \\ \hline
MPLS         & Multiprotocol Label Switching                \\ \hline
NASS         & Network As A Service                         \\ \hline
NGMN         & Next Generation Mobile Networks              \\ \hline
NSI          & Network Slice Instance                       \\ \hline
\added{ODU}  & \added{Optical Distribution Unit}            \\ \hline
ONF          & Open Networking Foundation                   \\ \hline
OSS          & Operation Support Systems                    \\ \hline
\added{PE}   & \added{Provider Edge}                        \\ \hline
QoS          & Quality of service                           \\ \hline
RAN          & Radio Access Network                         \\ \hline
SDN          & Software Defined Network                     \\ \hline
SI           & Service Instance                             \\ \hline
URLLC        & Ultra Reliable Low Latency Communications    \\ \hline
VSI          & Virtual switching Interfaces                 \\ \hline
\added{VPN}  & \added{Virtual Private Network}              \\ \hline
VRF          & Virtual Routing and Forwarding              \\ \hline
YANG         & Yet Another Next Generation                  \\ \hline
\end{tabular}
\end{table}

@@

The network slicing concept provides a framework for broad applicability across various industries. The majority of these scenarios envisioned to suit emerging and diverse business models based on the Network As A Service (NASS) approach, creating opportunities for intelligent services and a new business ecosystem \cite{kuklinski2019business,zhang2017network,khan2020network}.\deleted{,} One of the main enablers to drive the network slicing is the Fifth-generation (5G) networks realization. Due to the necessity to integrate multiple services with various performance requirements — such as high throughput, low latency, high reliability, high mobility, and high security — into a single physical network infrastructure, and provide each service with
a customized logical network. being the Network Slicing the key technology to achieve the aforementioned goals.

\replaced{5G expects to support a new generation of customer-tailored applications with diverse requirements regarding capacity, latency, level of mobility, number of users, and user density.  Hence, 5G sets the stage for innovation and transformation in customer services and vertical industries, such as the ones described in the}{Due to the 5G expectation of supporting of a new generation of customer-tailored applications with diverse and stringent requirements (e.g., in terms of capacity, latency, level of mobility, number of users, and user density), 5G sets the stage for innovation and transformation in consumer services and vertical industries, such as real-time services, location-based services, and mission-critical services, as the ones described in the} \Cref{TAB1} \cite{foukas2017network}.

\begin{table}[htb!]
\caption{Possible Applications derived from the 5G implementations.}
\label{TAB1}
\centering
\begin{tabular}{|l|l|l|}
\hline

@@

Despite the apparent advantages that an overlay MPLS tunnels could provide, there are some disadvantages. Overlay tunnels built by data encapsulation have neither visibility nor control of the underlying physical network. With more and more tunnels deployed on shared physical infrastructure, network congestion necessarily becomes an attention point.  Thus, VRFs, VSIs or \added{Optical Data units} (ODus) cannot be managed by their corresponding tenants directly because they are part of the same administrative domain represented by the physical device, and they need to be operated by the network administrator. Due to the massive number of tunnels and services in a complex network, the QoS and Traffic Engineering policies management becomes a crucial task to guarantee the right SLAs to its customers \cite{huang20205g,marotta2020reliable}.

@@

\begin{itemize}
    \item  \textit{Map \& Realize}:The mapping and realization can be done by the Domain controller applying the service logic to create policies directly on the Network elements.
\end{itemize}

@@

\added{A capture of the messages exchanged between the control items is depicted in \Cref{fig:sliceworkflow2}. The Figure illustrates in Orange the messages exchanged for the Network Slice Creation using the IETF network slices data model. The subsequent statements show how the SDTN controller unwrapped the creation request message to the optical and IP domains. It illustrates in red the IP network massages using gRPC, including the access ports, routing protocols, and PE-CE connectivity parameters. In purple, the T-API messages have the connectivity and optical service requirements.}

\added{The time consumed in the Slices creation was $10.34$ seconds on average. The \Cref{fig:sliceworkflow}.a depicts a cumulative histogram of the time consumed for the slice creation in the controller layer using ten samples. Additionally, the \Cref{fig:sliceworkflow}.b shows the percentage of time spent for the VPN-instantiation in the Virtual routers. The most time-consuming task is the BGP Neighbours creation ($13$ seconds), followed by the BGP instance redistribution ($10$ seconds). In contrast, the device implemented the primary VPN configuration parameters (Rute-Distinghuiser, Route Target and Router ID) in less than a second.}

@@

\begin{figure}[htb]
\includegraphics[width=\linewidth]{Figs/sliceworkflow2.png}
\caption{\added{Capture of the workflow used to instantiate the network slices in the network (Orange). The capture shows the IP network configuration (Red) and the T-API Optical domains (Purple).}}
\label{fig:sliceworkflow2}
\end{figure}

\begin{figure}[htb]
\includegraphics[width=\linewidth]{Figs/sliceworkflow.png}
\caption{\added{A cumulative step histogram of the time consumed for the slice creation, and the time consumed in during the VPN instantiation in the vRoutes. }}
\label{fig:sliceworkflow}
\end{figure}
